Regime transition identification for water governance at a basin scale

### 2020-11-25 tex/main/manuscript.tex
rectify a spelling mistake
sync in windows

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWGI index. 
	\textbf{A,} Change points detection. With sigificant change points in 1978 and 1994, the IWGI have three different periods in changing trend.
	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation have made the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWGI}
\end{figure}

@@

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item The socio-economic dominance may lead to further demands of water supply (S) because of increasing water withdrawals. However, an effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development along with the transformative trajectory, means:
		$$ Transformation \propto S^{-1} $$
		\item The transformation is usually accompanied by a tilt of purpose in water governance towards socio-economic services (usually non-provisioning purposes), because of higher returns:
		$$ Transformation. \propto P $$
		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
		\item The transformation usually lead to more complicated structure in water allocation, which is mainly a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
		$$ Transformation \propto A $$ 
	\end{itemize}

>>>>

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/index.pdf}
	\caption{Changes of the IWGI index. 
	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI have three different periods in changing trend.
	\textbf{B,} Contributions of each dimension to the changes of IWGI within three periods. Supply, purpose and allocation have made the main positive contributor of P1, P2 and P3, respectively.
	}
	\label{fig:IWGI}
\end{figure}

@@

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item The socio-economic dominance may lead to further demands of water supply (S) because of increasing water withdrawals. However, an effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development along with the transformative trajectory, means:
		$$ Transformation \propto S^{-1} $$
		\item The transformation is usually accompanied by a tilt of purpose in water governance towards socio-economic services (usually non-provisioning purposes), because of higher returns:
		$$ Transformation \propto P $$
		% - 社会发展通常伴随着更具结构性的水资源配置，如区域部门之间的分工合作，以及区域的统筹配置：
		\item The transformation usually lead to more complicated structure in water allocation, which is mainly a result of division and cooperation between regions and sectors because of environmental context and economic comparative advantages:
		$$ Transformation \propto A $$ 
	\end{itemize}
